The \dealii{} Library, Version 8.5

### 2017-03-10 8.5/paper.tex
Added more details to physics module, chiefly the sec on transformations

A dedicated physics module has been created to facilitate the
implementation of functions and classes that relate to continuum mechanics,
physical fields and material constitutive laws. To date, it includes
transformations of scalar or tensorial quantities between any two
configurations,
\marginpar{which configurations?}
and some definitions typically utilized in both linear and finite-strain
nonlinear elasticity.

The \verb!Physics::Transformations! namespace offers push-forward and
pull-back operations in the context of contravariant, covariant and Piola
transformations, as well as rotation operations for the Euclidean space. In
the \verb!Physics::Elasticity::Kinematics! namespace, a selection of
deformation, strain tensors and strain rate tensors are defined. The
\verb!Physics::Elasticity::StandardTensors! class provides some frequently
used second and fourth order metric tensors, and defines a number of
referential and spatial projection operators and tensor derivatives that
are commonly required in the definition of material laws.

>>>>

A dedicated physics module has been created to facilitate the
implementation of functions and classes that relate to continuum mechanics,
physical fields and material constitutive laws. To date, it includes
transformations of scalar or tensorial quantities between any two
configurations (by user-specification of a linear map $\mathbf{F}$), and some 
definitions typically utilized in both linear and finite-strain nonlinear 
elasticity.

The \verb!Physics::Transformations! namespace offers push-forward and
pull-back operations in the context of contravariant, covariant and Piola
transformations, as well as rotation operations for the Euclidean space. 
Although these transformations are defined in a general manner, one typical
use of them in finite-strain elasticity would be the determination of the 
Cauchy stress tensor $\boldsymbol{\sigma} = \boldsymbol{\sigma}\left(\mathbf{x}\right)$ 
defined at the spatial position $\mathbf{x} \in \mathcal{B}$ from its
fully referential counterpart, namely the Piola--Kirchhoff stress tensor 
$\mathbf{S} = \mathbf{S}\left(\mathbf{X}\right)$ computed at the material 
coordinate $\mathbf{X} \in \mathcal{B}_{0}$.
By choosing
$\mathbf{F} \left(\mathbf{X}\right) = \dfrac{\partial \mathbf{x}\left(\mathbf{X}\right)}{\partial \mathbf{X}}$,
this is achieved through the action of the Piola push-forward
$\boldsymbol{\sigma} = \dfrac{1}{\det \mathbf{F}} \, \mathbf{F} \cdot \mathbf{S} \cdot \mathbf{F}^{T}$.

In the \verb!Physics::Elasticity::Kinematics! namespace, a selection of
deformation, strain tensors and strain rate tensors are defined. The
\verb!Physics::Elasticity::StandardTensors! class provides some frequently
used second and fourth order metric tensors, and defines a number of
referential and spatial projection operators and tensor derivatives that
are commonly required in the definition of material laws.
